Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-17 paper/sec-analysis.tex
more work on draft

>>>>

In Table~\ref{tab:cutflowdetails}
we summarize the details of the cut flow of the present analysis,
separated into the exclusive boosted, intermediate
    and resolved categories.
    %
    From top to bottom, additional cuts are required in addition
    to the previous ones.
    %
    As we can see ....

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|c|c|c|}
\hline
&  Boosted  &   Intermediate &  Resolved  \\
\hline
\hline
C0 &  Generator level &  Generator level & Generator level \\
\hline
C1A & $N_{\rm jets}^{R}\ge 2$ & $N_{\rm jets}^{r}\ge 2$, $N_{\rm jets}^{R}=1$  &
 $N_{\rm jets}^{r}\ge 4$ \\
 C1B & +$p_T$ cuts & +$p_T$ cuts
 & +$p_T$ cuts \\
 C1C & + rapidity cuts &  + rapidity cuts &
 + rapidity cuts \\
 C1D & + Mass-Drop tag required & $N_{\rm jets}^{R}=1$ with MDT  &
  Higgs reco possible \\
C1E & $m_H$ window cut & $m_H$ window cut & $m_H$ window cut  \\
\hline
C2 & $b$-tagging  &  $b$-tagging &  $b$-tagging \\
\hline
  \end{tabular}
  \caption{\small Details of the cut flow of the present analysis in the boosted, intermediate
    and resolved categories.
    %
    See text for more details.
    \label{tab:cutflowdetails}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-17 paper/sec-pileup.tex
more work on draft

Up to know we have restricted ourselves to the study of the impact of PU
on signal distributions.
%
We now assess how the signal over background discrimination can be affected
in the presence of realistic PU conditions.

{\bf add plots signal vs background with PU}

>>>>

Up to know we have restricted ourselves to the study of the impact of PU
on signal distributions.
%
We now assess how the signal over background discrimination can be affected
in the presence of realistic PU conditions.
%
First of all let us consider the boosted category.
%
In Fig.~\ref{fig:signal-vs-back-boosted} we compare
various kinematical distributions for signal and background events,
     with and without PU: the invariant mass and the $p_T$ of the leading
     Higgs candidate, and the $\tau_{21}$ and $D^{(\beta)}_2$ substructure variables.
     %
     All these distributions correspond to the boosted category.
     %
     While for signal distributions the effects of PU after SK subtraction are small,
     differences are more marked for the background distributions, where
     the shapes of the distributions with and without background can be substantially
     different.
     %
     We note however that the fact that signal and background distribution exhibit
     rather different behaviors is maintained in the presence of PU.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \vspace{-1cm}
  \includegraphics[width=0.49\textwidth]{plots/m_h0_bst_comp_back.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_h0_bst_comp_back.pdf}
   \includegraphics[width=0.49\textwidth]{plots/tau21_h1_bst_comp_back.pdf}
  \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp_back.pdf}
   \caption{\small
     Comparison of kinematical distributions for signal and background events,
     with and without PU: the invariant mass and the $p_T$ of the leading
     Higgs candidate, and the $\tau_{21}$ and $D^{(\beta)}_2$ substructure variables.
     %
     All these distributions correspond to the boosted category.
}
\label{fig:signal-vs-back-boosted}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

Now we perform a similar comparison this time for
the resolved category.
